Flexibility of interactions depends on habitat suitability

### 2019-07-29 paper/manuscript.Rmd
Finishing Gravel 2018

**Is my central topic turnover of interactions**?

@@

**SHould I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**

@@

**From Gravel et al. 2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions. Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure. *Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe*

@@

@@

>>>>

**Is my central topic turnover of interactions**? If yes then I should quanitify turnover accross high and low suitability areas.

@@

**Continuation: Should I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**

**Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian. A better position in the grinellian niche allows for a larger Realised Eltonian niche.

@@

**From Gravel et al. 2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions. Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure. *Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe* -- for real ( They test prob. of two co-occurring species to interact does not depend on environment. I test single species thingy). Should I do that? suit sp.1 and suit sp. 2? It;s not about the environment, but about how the environment affect the species involved. Buya!

@@

Ecological interactions could also vary with the environment, P(Lijy | Ey ). Although it is rare to see a con- ditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment. For instance, McKinnon et al. (2010) showed that predation risks of shorebirds vary at the continental scale, decreasing from the south to the north. It is also common to see increasing top-down control with temperature (Shurin et al. 2012, Gray et al. 2016). Efects of the environment on interactions (Gibert and DeLong 2014) also propagate up the community and inluence net- work structure (Tylianakis et al. 2007, Petchey et al. 2010, Woodward et al. 2010).

In terms of species interacting with each other, our analysis suggests that the environment leaves a detectable imprint on species co-occurrence, but only a slight mark on the occurrence of realized links among species in a speciic place: the prob- ability of inding a given combination of species at a higher and a lower trophic level at the same site was clearly afected by the environment, whereas the probability of observing an interaction between the two was, given co-occurrence, not signiicantly so.

This does not imply that species will always interact when they meet – **although this is a basic assumption in most documented metawebs to date** (Havens 1992, Wood et al. 2015).

Evidence that the structure of ecological networks does vary across habitats (Tylianakis et al. 2007), over environmental gradients (Lurgi et al. 2012) and in time (Simanonok and Burkle 2014) is accumulating rapidly.

@@

Remarkable that we found a consistent signal of suitability given our relatively small number of communities and the multitude of processes that shape n. interactions Eltonian niche. We didn;t even account for traits. Interactions can influence co-occurrence (indirect and third order too see refs in Gravel 2018)
